Preliminary Thesis Defence

### 2013-11-22 draft.Rnw
fix autoref for equations by removing cleveref
twopage
change defence to defense

\documentclass[a4paper]{report}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage[authordate,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{Preliminary Thesis Defence\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
\end{tabular}
}

@@

\begin{refsection}
\chapter{Introduction}
In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:

@@

where equation (3.2) examines quantity and equation (3.3) quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.

>>>>

\documentclass[a4paper,twopage]{report}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[authordate,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{Preliminary Thesis Defense\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
\end{tabular}
}

@@

\begin{refsection}
\chapter{Introduction}
In this Preliminary Thesis Defense I present the research projects that I intend to use for my PhD dissertation. These projects are titled:

@@

where equation \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
